Information Disclosure in Dynamic Innovation Contests

### 2025-04-30 paper/Paper.tex
update-paper

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(y, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(y, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = y / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
\end{lemma}

@@

\section{Model Estimation}

@@

%% Data: Contest setting
The first component consists of essential contest details, including the contest duration, prize structure, information disclosure, and other governing rules.
Contrary to the assumptions of our model, a typical contest usually involves multiple teams rather than just two.
We index the participating teams of the contest by $i\in\{1, 2, ..., n\}$. 
To fully leverage the potential of the data and establish a connection with our theoretical model, let's assume that each participant perceives a competitor they are playing against at every moment, denoted as $j$. 
This perceived competitor is typically understood as the most prominent individual on the leaderboard, i.e., the person ranked first.
When team $i$ themselves hold the top position, their perceived competitor is the individual who poses the greatest threat, namely the person ranked second.
Furthermore, the contests may feature intricate prize structures, such as the provision of multiple awards, rather than adhering to a winner-takes-all format.
The issue will be discussed in Section~\ref{sec-kaggle-application}.

@@

By definition, the likelihood function of a realization of the representative player $i$'s submission events $\{t^i_k\}_{k=1}^{N_i}$ is given by 
\begin{equation}\label{eq-ihpp-prob}
p\left(\{\hat{t}^i_k\}_{k=1}^{N_i} | \tau_i\right) = \exp\left\{-\int_{s\in\mathcal{T}}\tau_i(s)ds\right\}\prod_{k=1}^{N_i}\tau_i(\hat{t}^i_k)
\end{equation}
where $\tau_i$ is defined in (\ref{eq-model-intensity}). 
Similar to the other player $j$.

Suppose we sample the leaderboard gap $\hat{y}_t$ at time points $(t_1, t_2, ..., t_N)$, obtaining observations $\{\hat{y}_{t_k}\}^N_{k=1}$. 
Moreover, we assume that the sampling occurs at fixed time intervals $t_{k+1}-t_k$. 
Let $t_0 = 0$ and suppose the initial gap $y_0$ follows $\mathcal{N}(\mu_0, \sigma_0)$. 
Then, according to the assumed data-generating process of $\hat{y}_t$ in (\ref{eq-leaderboard-gap}), the corresponding likelihood function is
\begin{equation}
\begin{aligned}
p&\left(\{\hat{y}_{t_k}\}_{k=1}^N | m_i, m_j\right) = 
\phi\left(y_0 | \mu_0, \sigma_0\right) \times\\
&\quad\prod_{k=0}^{N-1}\phi\left(\hat{y}_{t_{k+1}}-\hat{y}_{t_k}|\int_{t_k}^{t_{k+1}}m_i(\tilde{y}_s, s) - m_j(\tilde{y}_s, s)ds, \left(\sigma^2+\frac{1}{\lambda}\right)(t_{k+1}-t_k)\right)
\end{aligned}
\end{equation}

@@

A central challenge in generating synthetic data lies in dynamically constructing a point process that conforms to an inhomogeneous Poisson process.
We first generate candidate submission events according to a homogeneous Poisson process over the whole contest duration, using a fixed high intensity $\tau_i^\star \ge \sup_t \tau_i(t)$, and distribute them uniformly across the interval.
Then, we apply the classical thinning procedure \citep{lewis1979simulation} to determine whether each candidate event is accepted.

\begin{algorithm}
\caption{Synthetic Data Simulation}
\begin{algorithmic}
\STATE \textbf{Input:} 
	$\Delta t$, $T$, $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\tau^\star$
\STATE Sample $\{s_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from homogeneous Poisson process $(\tau^\star_{i(j)})$ on $[0, T)$
\STATE Sample $\{u_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from uniform distribution on $[0, 1]$
\STATE Sample a series of Brownian motion $(\hat{W}_t)$
\STATE Initialize $\ell^{i(j)}=0$, $y_0 = 0$, $\hat{y}_0 = 0$, $\tilde{y}_t=0$
\FOR{$t = 0$ to $T$}
    \STATE $m_{i(j)}(\tilde{y}_t, t)$  $\gets$ (\ref{eq-equilibrium-effort}), $\tau^{i(j)}(t)$ $\gets$ (\ref{eq-model-intensity})
    \STATE $y_{t+\Delta t} \gets$ (\ref{eq-state-dynamics}); $\tilde{y}_{t+\Delta t}$ $\gets$ (\ref{eq-fintered-y-update})
    \FOR{$s_{k}^{i(j)} \in [t, t+\Delta t)$} 
        \IF {$u_k^{i(j)} < \tau_{i(j)}(s_{k}^{i(j)}) / \tau^\star_{i(j)}$}
        	    \STATE $\hat{t}^{i(j)}_{\ell} \gets s_{k}^{i(j)}$; $\ell^{i(j)} \gets \ell^{i(j)}+1$
	    \hfill \COMMENT{Accept the submission event}
	    \STATE $\hat{y}_{t+\Delta t} \gets $ (\ref{eq-leaderboard-gap})
        \ENDIF
    \ENDFOR
\ENDFOR
\STATE Fill in all missing entries in $(\hat{y}_t)$ by propagating the last observed value.
\STATE \textbf{Output:} $(\tilde{y}_t)$, $(\hat{y}_t)$, $\{\hat{t}_k^{i(j)}\}^{N_{i(j)}}_{k=1}$, $(m_{i(j)}(\tilde{y}_t, t))$
\end{algorithmic}
\end{algorithm}

>>>>

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
\end{lemma}

@@

\section{Estimation}

@@

%% Data: Contest setting
The first component consists of essential contest details, including the contest duration, prize structure, information disclosure policy, and other governing rules.
Contrary to the assumptions of our model, a typical contest usually involves multiple teams rather than just two.
We index the participating teams of the contest by $i\in\{1, 2, ..., n\}$. 
To fully leverage the potential of the data and establish a connection with our theoretical model, let's assume that each participant perceives a competitor they are playing against at every moment, denoted as $j$. 
This perceived competitor is typically understood as the most prominent individual on the leaderboard, i.e., the person ranked first.
When team $i$ themselves hold the top position, their perceived competitor is the individual who poses the greatest threat, namely the person ranked second.
Furthermore, the contests may feature intricate prize structures, such as the provision of multiple awards, rather than adhering to a winner-takes-all format.
The issue will be discussed in Section~\ref{sec-kaggle-application}.

@@

By definition, the likelihood function of a realization of the representative player $i$'s submission events $\{t^i_k\}_{k=1}^{N_i}$ is given by 
\begin{equation}\label{eq-ihpp-prob}
p\left(\{\hat{t}^i_k\}_{k=1}^{N_i} | \tau_i\right) = \exp\left\{-\int_{s\in\mathcal{T}}\tau_i(s)ds\right\}\prod_{k=1}^{N_i}\tau_i(\hat{t}^i_k)
\end{equation}
where $\tau_i$ is defined in (\ref{eq-model-intensity}). 
Similar to the other player $j$. 
Next, suppose we sample the leaderboard gap $\hat{y}_t$ at time points $(t_1, t_2, ..., t_N)$, obtaining observations $\{\hat{y}_{t_k}\}^N_{k=1}$. 
Let $t_0 = 0$ and suppose the initial gap $y_0$ follows $\mathcal{N}(\mu_0, \sigma_0)$. 
Then, according to the assumed data-generating process of $\hat{y}_t$ in (\ref{eq-leaderboard-gap}), the corresponding likelihood function is
\begin{equation}\label{eq-obs_gap-prob}
\begin{aligned}
p&\left(\{\hat{y}_{t_k}\}_{k=1}^N | m_i, m_j\right) = 
\phi\left(y_0 | \mu_0, \sigma_0\right) \times\\
&\quad\prod_{k=0}^{N-1}\phi\left(\hat{y}_{t_{k+1}}-\hat{y}_{t_k}|\int_{t_k}^{t_{k+1}}m_i(\tilde{y}_s, s) - m_j(\tilde{y}_s, s)ds, \left(\sigma^2+\frac{1}{\lambda}\right)(t_{k+1}-t_k)\right)
\end{aligned}
\end{equation}
where $\hat{y}_{t_0} = y_0$. 
Here, we assume that time is discretized into uniform intervals of length $\Delta$, so that the integrals in the above equations can be approximated by summations.

To evaluate the likelihood functions (\ref{eq-ihpp-prob}) and (\ref{eq-obs_gap-prob}), we must first compute the equilibrium trajectories of both the perceived output gap $(\tilde{y}_t)$ and the effort levels $(m_i(\tilde{y}_t, t), m_j(\tilde{y}_t, t))$, as implied by equations (\ref{eq-equilibrium-effort}) and (\ref{eq-fintered-y-update}). 
Importantly, the construction of $\tilde{y}$ and the effort functions $m_i$ and $m_j$ depends on the underlying (unobserved) parameters $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\mu_0$ and $\sigma_0$, which are themselves subject to estimation.
We denote these underlying parameters collectively as $\mathcal{P}$.

Once these parameters are specified, the equilibrium paths of the perceived output gap $(\tilde{y}_t)$ and the corresponding effort levels $(m_i(\tilde{y}_t, t), m_j(\tilde{y}t, t))$ can be deterministically computed. 
However, evaluating $m_{i(j)}(\tilde{y}_t, t)$ via equation~(\ref{eq-equilibrium-effort}) requires numerically approximating the inverse function $\gamma^{-1}$, which poses challenges for the use of gradient-based Markov Chain Monte Carlo (MCMC) sampling methods, such as Hamiltonian Monte Carlo (HMC) and the No-U-Turn Sampler (NUTS).
Hence, we approximate this inverse function with an analytical form\footnote{The parameter $a = 0.856$ is obtained by minimizing the infinity norm of the difference between the numerical inverse of $\gamma(\cdot)$ and the approximation $\frac{2}{\pi} \arctan(a x)$.
The resulting maximum approximation error, measured in the infinity norm, is approximately 0.019.}:
\begin{equation}\label{eq-invgamma-approx}
\gamma^{-1}(x) \approx \frac{2}{\pi}\arctan(0.856 \cdot x)
\end{equation}
Figure~\ref{fig-approximation} compares the equilibrium effort function $m_i(\tilde{y}_t, t)$ derived from the approximate analytical form of $\gamma^{-1}$ in equation~(\ref{eq-invgamma-approx}) with that obtained from the numerically accurate solution.
As illustrated, the approximation closely replicates the true function.

\begin{figure}[!ht]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{approx_invgamma.pdf}
        \caption{Auxiliary Function $\gamma^{-1}(x)$}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{approx_equi_effort.pdf}
        \caption{Equilibrium Effort $m_i(\tilde{y}_t, t)$}
    \end{subfigure}
    \caption{Comparison of the Accurate and Approximate Forms ($\theta = 1$, $c_i = c_j = 1$, $\sigma=1$, $\Delta=1/24$)}
    \label{fig-approximation}
\end{figure}

@@

A central challenge in generating synthetic data lies in dynamically constructing a point process that conforms to an inhomogeneous Poisson process.
We first generate candidate submission events according to a homogeneous Poisson process over the whole contest duration, using a fixed high intensity $\tau^\star \ge \sup_t \tau_{i(j)}(t)$.
Then, we apply the classical thinning procedure \citep{lewis1979simulation} to determine whether each candidate event is accepted.

\begin{algorithm}
\caption{Synthetic Data Simulation}
\begin{algorithmic}
\STATE \textbf{Input:} 
	$\Delta$, $T$, $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\tau^\star$, $y_0$, $\mu_0$
\STATE Sample $\{s_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from homogeneous Poisson process $(\tau^\star_{i(j)})$ on $[0, T)$
\STATE Sample $\{u_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from uniform distribution on $[0, 1]$
\STATE Sample series of Brownian motions $(W_t)$ and $(B_t)$
\STATE Initialize $\ell^{i(j)}=0$, $\hat{y}_0 = 0$, $\tilde{y}_t=\mu_0$
\FOR{$t = 0$ to $T$}
    \STATE $m_{i(j)}(\tilde{y}_t, t)$  $\gets$ (\ref{eq-equilibrium-effort}), $\tau^{i(j)}(t)$ $\gets$ (\ref{eq-model-intensity})
    \hfill \COMMENT{Use $\theta$, $c_{i(j)}$, $\sigma$, $r$, $T$}
    \STATE $y_{t+\Delta} \gets$ (\ref{eq-state-dynamics}); $\tilde{y}_{t+\Delta}$ $\gets$ (\ref{eq-fintered-y-update})
    \hfill \COMMENT{Use $\sigma$, $\lambda$, $\Delta$, $W_{t+\Delta}$}
    \FOR{$s_{k}^{i(j)} \in [t, t+\Delta)$} 
        \IF {$u_k^{i(j)} < \tau_{i(j)}(s_{k}^{i(j)}) / \tau^\star_{i(j)}$}
        	    \STATE $\hat{t}^{i(j)}_{\ell} \gets s_{k}^{i(j)}$; $\ell^{i(j)} \gets \ell^{i(j)}+1$
	    \hfill \COMMENT{Accept the submission event}
	    \STATE $\hat{y}_{t+\Delta} \gets $ (\ref{eq-leaderboard-gap})
	    \hfill \COMMENT{Use $\sigma$, $\lambda$, $B_{t+\Delta}$}
        \ENDIF
    \ENDFOR
\ENDFOR
\STATE Fill in all missing entries in $(\hat{y}_t)$ by propagating the last observed value.
\STATE \textbf{Output:} $(\tilde{y}_t)$, $(\hat{y}_t)$, $\{\hat{t}_k^{i(j)}\}^{N_{i(j)}}_{k=1}$, $(m_{i(j)}(\tilde{y}_t, t))$
\end{algorithmic}
\end{algorithm}
